%-------------------------
% Resume in Latex
% Author : Ashutosh Tiwari
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames, dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{ \vspace{-2pt}\scshape\raggedright\large }{}{0em}{}[
\color{black}
\titlerule
\vspace{-3pt}
]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{ \item\small{ {#1 \vspace{-2pt}} } }

\newcommand{\resumeSubheading}[4]{
\vspace{1pt}
\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
	\textbf{#1}       & #2                 \\
	\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}
\vspace{-3pt}
}

\newcommand{\resumeSubSubheading}[2]{ \item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
	\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}
\vspace{-2pt}
}

\newcommand{\resumeProjectHeading}[2]{ \item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
	\small#1 & #2 \\
\end{tabular*}
\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}
\vspace{-2pt}}

\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}
\vspace{-2pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%

\begin{document}
	\begin{center}
		{\Huge \scshape Ashutosh \textbf{Tiwari}} \\
		\vspace{8pt}
		\small +xx-xxxxxxxxxx $|$
		\href{mailto:xxxx@xxxx.xxxx}{\underline{xxxx@xxxx.xxxx}}
		$|$
		\href{https://linkedin.com/in/iashutoshtiwari}{\underline{linkedin.com/in/iashutoshtiwari}}
		$|$
		\href{https://github.com/iashutoshtiwari}{\underline{github.com/iashutoshtiwari}}
	\end{center}

	%-----------PROGRAMMING SKILLS-----------
	\section{Skills}
	\begin{itemize}[leftmargin=0.15in, label={}]
		\small{\item{ \textbf{Languages}{: JavaScript, Java, C++, Python}\vspace{2pt} \\ \textbf{Technologies and Frameworks}{: React, Redux, Node.js, Next.js, Express}\vspace{2pt} \\ \textbf{Other}{: Git, RESTful API, Problem solving, Data structures and algorithms. }\vspace{2pt}\vspace{2pt} }}
	\end{itemize}

	%-----------EXPERIENCE--------------------
	\section{Experience}
	\resumeSubHeadingListStart

	\resumeSubheading {Member of Technical Staff}{Aug. 2021 -- Present} {Mindstix Software Labs}{Pune, MH}
	\resumeItemListStart \resumeItem
	{Part of the team responsible for the development of end-to-end e-commerce solutions for Staples Inc. and Amway Taiwan.}
	\resumeItem
	{Responsible for implementing new features, supporting existing components, and fixing bugs for cart, checkout, payment, and order confirmation pages.}
	\resumeItem
	{Created high-quality and responsive UI components using React, Redux, and NextJS framework.}
	\resumeItem
	{Worked on multiple 3rd-party payment integrations including PayPal, VISA, and Apple Pay across projects.}
	\resumeItem
	{Ensured accessibility and cross-browser compatibility of the web pages in compliance with the Americans with Disabilities Act (ADA) and other standards.}
	\resumeItem {Mentored new team members as SME for cart-checkout domain.}
	\resumeItem
	{Integrated backend APIs with the frontend and created Node layer APIs to format and combine client’s API(s) response as per requirements.}
	\resumeItem
	{Integrated Google’s reCAPTCHA v3 in the Amway application to prevent bots and enhance security.}
	\resumeItem
	{Developed the new Rewards program for cart and checkout for Staples Inc., which increased customer loyalty and retention.}
	\resumeItem
	{Worked on the end-to-end redesign of Staples's checkout page for all view-ports, along with improving overall core web vitals of the page.}
	\resumeItemListEnd

	\resumeSubheading {Programmer Analyst Trainee}{Aug. 2020 -- Mar. 2021}
	{Cognizant}{Coimbatore, TN} \resumeItemListStart \resumeItem {Worked on the e-commerce application of a retail fashion company as part of the product discovery and merchandising Pod.}
	\resumeItem {Implemented product search functionality.} \resumeItem {Worked on product discovery features such as sort and filter.}
	\resumeItemListEnd

	\resumeSubheading {Intern}{Jan. 2020 -- May. 2020} {Cognizant}{Pune, MH}
	\resumeItemListStart \resumeItem
	{Completed training in various frontend technologies and languages such as HTML5, CSS3, JavaScript, React, Redux, Webpack and SASS gaining proficiency and confidence in web development.}
	\resumeItem
	{Developed a small e-commerce application using React and Redux with a team of 4 members as a capstone project.}
	\resumeItem
	{Learned and applied best practices and standards for coding, testing, and documentation, following the agile methodology and using tools such as Git, Jira.}
	\resumeItemListEnd

	\resumeSubHeadingListEnd

	%-----------EDUCATION-----------
	\section{Education}
	\resumeSubHeadingListStart \resumeSubheading {Chandigarh University}{Mohali, PB}
	{Bachelor of Engineering in Computer Science}{August 2016 -- July 2020}
	\resumeSubHeadingListEnd

	%-----------PROJECTS-----------

	% \section{Projects}
	%     \resumeSubHeadingListStart
	%       \resumeProjectHeading
	%           {\textbf{Gitlytics} $|$ \emph{Python, Flask, React, PostgreSQL, Docker}}{June 2020 -- Present}
	%           \resumeItemListStart
	%             \resumeItem{Developed a full-stack web application using with Flask serving a REST API with React as the frontend}
	%             \resumeItem{Implemented GitHub OAuth to get data from user’s repositories}
	%             \resumeItem{Visualized GitHub data to show collaboration}
	%             \resumeItem{Used Celery and Redis for asynchronous tasks}
	%           \resumeItemListEnd
	%       \resumeProjectHeading
	%           {\textbf{Simple Paintball} $|$ \emph{Spigot API, Java, Maven, TravisCI, Git}}{May 2018 -- May 2020}
	%           \resumeItemListStart
	%             \resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job}
	%             \resumeItem{Published plugin to websites gaining 2K+ downloads and an average 4.5/5-star review}
	%             \resumeItem{Implemented continuous delivery using TravisCI to build the plugin upon new a release}
	%             \resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin}
	%           \resumeItemListEnd
	%     \resumeSubHeadingListEnd

	%-------------------------------------------
\end{document}